---
title: "R Basics Practice Problem Solutions"
author: "|# Dominic Owusu Abeyie #|"
#institute: "KNUST"
#date: ""  
output:
  beamer_presentation:
    colortheme: "dolphin"
    fonttheme: "structurebold"
  ioslides_presentation: default
header-includes:
  - \usepackage{graphicx}  
  - \usepackage{xcolor}    
  - \AtBeginDocument{
      \titlegraphic{\includegraphics[width=2cm]{University_of_Chicago_shield.png} \\ 
      {\small \textcolor{blue}{Data Science for Research Assistants - UChicago}}}
    }
  - \AtBeginDocument{\date{03-12-2024}} 
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## ISLR Chapter 2 Q8

- (a) Set **wd** and load college data  
```{r, echo=TRUE, eval=FALSE}
setwd("~/Dropbox/Github/R/R Module 1 Basics)  
college <- read.csv(file="College.csv", header = TRUE)
```

```{r}
setwd("C:/Users/dowus/Dropbox/Github Files/Data Science for Research Assistants - University of Chicago/Data_Science_for_Research_Assistants_R_and_STATA_UChicago/R/R Module 1 Basics")
college <- read.csv(file="College.csv", header = TRUE, sep = ",")

```

## ISLR Chapter 2 Q8

- (b,c) Give data frame college rownames and delete first column afterward.

```{r, echo=TRUE}
rownames(college) <- college[,1]
college <- college[,-1]
#View(college)

```

## ISLR Chapter 2 Q8
- Summary of variables: There are 19 variables. This produces summary of 2 variables in order to fit the page. #The rest can produced by subsetting the data.

```{r, echo = TRUE}
summary(college[,1:2])

```

## ISLR Chapter 2 Q8
- Summary of variables: _continue_...
```{r, echo=TRUE}
summary(college[,3:5])
```

## ISLR Chapter 2 Q8


```{r, echo=TRUE}
#Visualize scatter plot of first 10 var.
pairs(college[, 2:11]) 
```

## ISLR Chapter 2 Q8

### Boxplot Code  

```{r, echo=TRUE, eval=FALSE}

college$Private <- as.factor(college$Private)

plot(college$Private, college$Outstate, 
     main = "Outstate Tuition vs Private/Public Colleges",
     xlab = "Private College", 
     ylab = "Out-of-State Tuition",
     col = "lightblue")
```
## ISLR Chapter 2 Q8

- Visualize boxplot
```{r, echo=FALSE}
college$Private <- as.factor(college$Private)
plot(college$Private, college$Outstate, 
     main = "Outstate Tuition vs Private/Public Colleges",
     xlab = "Private College", 
     ylab = "Out-of-State Tuition",
     col = "lightblue")

```

## ISLR Chapter 2 Q8

- Create a new qualitative variable (“Yes” or “No”), called Elite

```{r, echo=FALSE}
Elite <- rep("No", nrow(college))
Elite[college$Top10perc > 50] <- "Yes"
Elite <- as.factor(Elite)
college <- data.frame(college, Elite)
```

```{r, echo=TRUE, eval=FALSE}
Elite <- rep("No", nrow(college))
Elite[college$Top10perc > 50] <- "Yes"
Elite <- as.factor(Elite)
college <- data.frame(college, Elite)
```

```{r, echo=TRUE}
# Check how many elite colleges exist
summary(Elite)
```

## ISLR Chapter 2 Q8

- Code of boxplots for Outstate vs Elite

```{r, echo=TRUE, eval=FALSE}
plot(college$Elite, college$Outstate, 
     main = "Outstate Tuition for Elite vs 
     Non-Elite Colleges",
     xlab = "Elite Status",
     ylab = "Out-of-State Tuition",
     col = "lightblue")
```

## ISLR Chapter 2 Q8

- Boxplots for Outstate vs Elite

```{r, echo=FALSE}
plot(college$Elite, college$Outstate, 
     main = "Outstate Tuition for Elite vs Non-Elite Colleges",
     xlab = "Elite Status",
     ylab = "Out-of-State Tuition",
     col = "lightblue")
```
